\documentclass{article}
\title{TCP Worcester Reinforcement Learning Classifier Algorithm}
\author{Dolan Murvihill}
\date{\today}

\usepackage{amsmath}

\begin{document}
\maketitle
\section{Introduction}
\section{Design Criteria}
\section{Input}
The input to the TCPW Classifier is a TCPW \textit{state}, a corresponding
TCPW \textit{action} which was taken in that state, and a sequence of
\textit{events} which occurred as a result of that action. States are equivalent
to the states used in Remy.
A \textit{state} consists of:
\begin{quote}
  \begin{itemize}
  \item An exponentially-weighted moving average (EWMA) of the interarrival time
    between new acknowledgments received (\texttt{ack\_ewma})
  \item An exponentially-weighted moving average of the time between TCP sender
    timestamps reflected in those acknowledgments(\texttt{send\_ewma}). A weight
    of 1/8 is given to the new sample in both EWMAs.
  \item The ratio between the most recent RTT and the minimum RTT seen during
    the current connection (\texttt{rtt\_ratio}).
  \end{itemize}
\end{quote} (From Winstein and Balakrishnan)

An \textit{action} is either $nosend$ or a packet $P_i$ to send, chosen from
the host's send queue.

An \textit{event} is a list of chronologically ordered
\textit{node transit reports},  and an \textit{end-to-end report}. Each node
transit report is information about events that occurred while the packet was
waiting in a buffer. It contains:
\begin{itemize}
  \item A list of packets dropped while $P_i$ was waiting in that buffer.
  \item The amount of time the packet spent waiting for transit.
\end{itemize}
An end-to-end report is information about the overall status of the packet. It
contains:
\begin{itemize}
  \item The total amount of time the packet spent in the network.
  \item The number of hops the packet took.
  \item The ultimate fate of the packet (chosen from \{\textit{received},
    \textit{dropped}, \textit{corrupted}, \textit{refused}\}).
\end{itemize}

\section{Output}
TCPW classifier returns a real value $U$, where $U$ represents the utility
gained from performing the action under the given state.
\section{Requirements}
The utility from an action of $nosend$ is zero. The utility from
an action of $P_i$ is based on the events that occurred while $P_i$ was in
transit:
\begin{itemize}
  \item For successfully transiting the network and reaching the destination,
    $U$ is set to $\alpha$.
  \item For each packet that was dropped from a queue that $P_i$ was in, $U$ is
    penalized by $\beta$.
  \item If $P_i$ was dropped, $U$ is penalized by a value $\gamma$.
\end{itemize}
\end{document}
